Late and early effective start of non-pharmaceutical interventions inferred during COVID-19 outbreaks

### 2020-05-11 ms/ms.tex
finished abstract

% Abstract
\begin{abstract}
During February and March 2020, several countries implemented a variety of non-pharmaceutical interventions with variable schedules to control the COVID\=/-19 pandemic caused by the SARA\=/CoV\=/2 virus.
Overall, these interventions have successfully reduced the ...
\end{abstract}

>>>>

% Abstract
\begin{abstract}

During February and March 2020, several countries implemented non-pharmaceutical interventions, such as school closures and lockdowns, with variable schedules to control the COVID\=/-19 pandemic caused by the SARA\=/CoV\=/2 virus.
Overall, these interventions seem to have successfully reduced the spread of the pandemic.
We hypothesize that the official and effective start date of such interventions can significantly differ, for example due to slow diffusion of guidelines in the population, or due to unpreparedness of the authorities and the public.
We use an SEIR epidemiological model and an MCMC inference framework to estimate the effective start of NPIs in several countries, and compare this effective dates to the official dates.
We report our finding of both late and early effects of NPIs, and discuss potential causes and consequences of our results.

\end{abstract}
